Title

### 2016-11-24 paper.tex
Fixed bug in merge.. git sucks for tex

The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs (Figure~\ref{fig3:graph}).
It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.

>>>>

The Ordered Decomposition DAGs kernel framework (ODD)~\cite{Dasan2012} considers as non-zero features in the RKHS the trees that appear as subtrees of the input graphs.
It exploits the shortest-path (up to length $\eta$) DAG decompositions starting from each node in the graph to generate DAG structures, and then extracts tree features from them.
Each tree-feature is weighted as $f \cdot \lambda^{dim}$, where $f$ is the frequency of the feature, $dim$ its dimension (the number of vertices in the tree) and $\lambda>0$ a weighting parameter.
The time complexity of the main representative of this family, ODD$_{ST}$, is, under mild conditions, $O(|V_G| \log |V_G|)$, and the number of generated features for a graph is at most $|V_G|\rho^\eta$.
